Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-19 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
fixing  typos

\ab{The ParSpec framework was introduced in Ref.~\cite{Maselli:2019mjd} and can be used to our purpose. It is} an observable-based
bivariate expansion of Eq.~\eqref{eq:general_deviation}, given by
%
\begin{subequations}
\label{eq:kerr_expansion}
\begin{align}
\omega_{\ell m n} &= \frac{1}{M_{\rm f}} \sum_{j = 0}^{N_{\rm max}} \, \chi_{\rm f}^{j} \omega^{(j)}_{\ell m n} \, \left( 1 + \gamma\, \delta \omega^{(j)}_{\ell m n} \right), \\
\tau_{\ell m n}   &= M_{\rm f}     \sum_{j = 0}^{N_{\rm max}} \, \chi_{\rm f}^{j} \tau^{(j)}_{\ell m n}   \, \left( 1 + \gamma\, \delta \tau^{(j)}_{\ell m n} \right),
\end{align}
\end{subequations}
%
\ab{where $M_{\rm f}$ and $\chi_{\rm f}$ are the detector-frame final mass and spin, respectively;}
the quantities $\omega_{\ell m n}^{(j)}$ and $\tau_{\ell m n}^{(j)}$ are dimensionless coefficients of the
expansion in spin for BH QNMs in GR, while $\delta\omega_{\ell m n}^{(j)}$ and $\delta\tau_{\ell m n}^{(j)}$ are
source-independent dimensionless coefficients that characterize the corrections to the GR QNM at
each spin-order,
%
and $N_{\rm max}$ is the order of the spin expansion.
%
All source dependence for a given modified gravity theory is contained in the
dimensionless parameter $\gamma$, which reads
%
\begin{equation}
\gamma
%
= \left(\frac{\ell_{\rm th}}{M^{\rm s}_{\rm f}}\right)^{p}
%
= \left[
\frac{\ell c^2 (1 + z)}{G M_{\rm f}}
\right]^{p},
\label{eq:def_gamma}
\end{equation}
%
which depends on \ab{the length-scale parameter $\ell_{\rm th}$ of the specific gravity theory
(non-GR modifications become important at distances $\lesssim \ell_{\rm th}$), and
the exponent $p$ is related to how the non-GR modifications are
added to the Einstein-Hilbert action.}
%
In Eq.~\eqref{eq:def_gamma} we made $\gamma$ dimensionless by using the other
length-scale associated with the remnant black hole (i.e., its source-frame mass
$M^{\rm s}_{\rm f}$\footnote{Throughout this paper, we maintain the convention of
using the upperscript ``s" to denote source-frame quantities and plain baseline
symbols for detector-frame measurements.}), which we can also write in terms of the detector-frame mass $M_{\rm f}$
through the redshift $z$~\cite{Krolak:1987ofj}. Also, dividing by the factor $G/c^2$ allows us to
express $\ell$ in physically intuitive metric units.

@@

The GW signal from a \ab{quasicircular} BBH can be \ab{described} \sout{determined} in GR by a unique set of
parameters $\bm{\theta}$, that includes the masses and spins of the two BHs,
$(m_1,\, m_2,\, \mathbf{S}_1,\, \mathbf{S}_2)$, the sky location determined by the
luminosity distance $D_L$\abcomm{I changed to capital $d$ because later we call the
data ``d''.}, right ascension $\alpha$ and declination $\delta$,
and the orientation of the binary given by the inclination $\iota$ and polarization $\psi$
angles.
%
The set is completed by the choice of a reference time $t_0$ and phase
$\phi_0$. If we further assume that the spins of the individual BHs are
restricted to be \sout{parallel} \ab{aligned or anti-aligned (for short, aligned)} to the unit vector
perpendicular to the orbital plane ($\mathbf{\hat{L}}$), we reduce the six
components of the spins to just two, $\chi_i \equiv \mathbf{S}_i\cdot \mathbf{\hat{L}} /m_i^2$ with $i = 1,2$,
and our entire parameter set from 15 to 11.
%
Let us also define some additional parameters and set some conventions that
will be useful in our analysis later, namely, the total mass
%
$M=m_1+m_2$,
%
the chirp mass
%
$\mathcal {M}=(m_{1}m_{2})^{3/5}/(m_{1}+m_{2})^{1/5}$,
%
the asymmetric mass ratio $q=m_1/m_2$, with the convention $m_1 \geqslant m_2$ (and thus $q \geqslant 1$),
and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$. \ab{Note that for BHs $-1 \leq \chi_i \leq 1$.}

>>>>

\ab{The ParSpec framework was introduced in Ref.~\cite{Maselli:2019mjd} and can be used to our purpose. It is} an observable-based
bivariate expansion of Eq.~\eqref{eq:general_deviation}, given by
%
\begin{subequations}
\label{eq:kerr_expansion}
\begin{align}
\omega_{\ell m n} &= \frac{1}{M_{\rm f}} \sum_{j = 0}^{N_{\rm max}} \, \chi_{\rm f}^{j} \omega^{(j)}_{\ell m n} \, \left( 1 + \gamma\, \delta \omega^{(j)}_{\ell m n} \right), \\
\tau_{\ell m n}   &= M_{\rm f}     \sum_{j = 0}^{N_{\rm max}} \, \chi_{\rm f}^{j} \tau^{(j)}_{\ell m n}   \, \left( 1 + \gamma\, \delta \tau^{(j)}_{\ell m n} \right),
\end{align}
\end{subequations}
%
\ab{where $M_{\rm f}$ and $\chi_{\rm f}$ are the detector-frame final mass and spin, respectively;}
the quantities $\omega_{\ell m n}^{(j)}$ and $\tau_{\ell m n}^{(j)}$ are dimensionless coefficients of the
expansion in spin for BH QNMs in GR, while $\delta\omega_{\ell m n}^{(j)}$ and $\delta\tau_{\ell m n}^{(j)}$ are
source-independent dimensionless coefficients that characterize the corrections to the GR QNM at
each spin-order,
%
and $N_{\rm max}$ is the order of the spin expansion.
%
All source dependence for a given modified gravity theory is contained in the
dimensionless parameter $\gamma$, which reads
%
\begin{equation}
\gamma
%
= \left(\frac{\ell_{\rm th}}{M^{\rm s}_{\rm f}}\right)^{p}
%
= \left[
\frac{\ell_{\rm th} c^2 (1 + z)}{G M_{\rm f}}
\right]^{p},
\label{eq:def_gamma}
\end{equation}
%
which depends on \ab{the length-scale parameter $\ell_{\rm th}$ of the specific gravity theory
(non-GR modifications become important at distances $\lesssim \ell_{\rm th}$), and
the exponent $p$ is related to how the non-GR modifications are
added to the Einstein-Hilbert action.}
%
In Eq.~\eqref{eq:def_gamma} we made $\gamma$ dimensionless by using the other
length-scale associated with the remnant black hole (i.e., its source-frame mass
$M^{\rm s}_{\rm f}$\footnote{Throughout this paper, we maintain the convention of
using the upperscript ``s" to denote source-frame quantities and plain baseline
symbols for detector-frame measurements.}), which we can also write in terms of the detector-frame mass $M_{\rm f}$
through the redshift $z$~\cite{Krolak:1987ofj}. Also, dividing by the factor $G/c^2$ allows us to
express $\ell$ in physically intuitive metric units.

@@

The GW signal from a \ab{quasicircular} BBH can be \ab{described} \sout{determined} in GR by a unique set of
parameters $\bm{\theta}$, that includes the masses and spins of the two BHs,
$(m_1,\, m_2,\, \mathbf{S}_1,\, \mathbf{S}_2)$, the sky location determined by the
luminosity distance $D_L$\abcomm{I changed to capital $d$ because later we call the
data ``d''.}, right ascension $\alpha$ and declination $\delta$,
and the orientation of the binary given by the inclination $\iota$ and polarization $\psi$
angles.
%
The set is completed by the choice of a reference time $t_0$ and phase
$\phi_0$. If we further assume that the spins of the individual BHs are
restricted to be \sout{parallel} \ab{aligned or anti-aligned (for short, aligned) to the unit vector
perpendicular to the orbital plane ($\mathbf{\hat{L}}$), we reduce the six
components of the spins to just two, $\chi_i \equiv \mathbf{S}_i\cdot \mathbf{\hat{L}} /m_i^2$ with $i = 1,2$,
and our entire parameter set from 15 to 11.}
%
Let us also define some additional parameters and set some conventions that
will be useful in our analysis later, namely, the total mass
%
$M=m_1+m_2$,
%
the chirp mass
%
$\mathcal {M}=(m_{1}m_{2})^{3/5}/(m_{1}+m_{2})^{1/5}$,
%
the asymmetric mass ratio $q=m_1/m_2$, with the convention $m_1 \geqslant m_2$ (and thus $q \geqslant 1$),
and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$. \ab{Note that for BHs $-1 \leq \chi_i \leq 1$.}
